The Power of Two Random Choices\\ \large A follow up seminar to the Parallel Algorithms lecture\footnote{Jesper Larsson Träff, lecture ``Parallel Algorithms'', 2012 winter term at TU Wien.}

### 2014-01-27 article/article.tex
intro and structure of analysis

\begin{theorem}
Consider any sequence of insertions and deletions s.t.~at most $hn$ balls are in the bins at any time. If the balls are placed into bins by the Greedy algorithm, at any time $t$ the maximum load is at most 
\[
\frac{m}{n} + \Theta\left(\frac{\log \log n}{\log d} \right)
\]
w.h.p.~at any time $t$ \cite{ABKU99} \cite{BCSV06}.

@@

\begin{theorem}
If $n$ balls are placed into $n$ bins using the Always-go-left scheme, the number of balls in the fullest bin will be 
\[
\frac{\ln\ln n}{d \ln \Phi_d} \pm \Theta(1)
\]
w.h.p.
\end{theorem}

\begin{theorem}
Consider any sequence of insertions and deletions s.t.~at most $hn$ balls are in the bins at any time. If the balls are placed into bins by the Greedy algorithm, at any time $t$ the maximum load is at most 
\[
\frac{\ln\ln n}{d \ln \Phi_d} + O(h)
\]
w.h.p.
\end{theorem}

\section{Analysis}
\label{sec:analysis}

@@

>>>>

\begin{theorem}
\label{theorem:greedy}
Consider any sequence of insertions and deletions s.t.~at most $hn$ balls are in the bins at any time. If the balls are placed into bins by the Greedy algorithm, at any time $t$ the maximum load is at most 
\[
\frac{m}{n} + \Theta\left(\frac{\log \log n}{\log d} \right)
\]
w.h.p.~at any time $t$ \cite{ABKU99} \cite{BCSV06}.

@@

\begin{theorem}
\label{theorem:agln}
If $n$ balls are placed into $n$ bins using the Always-go-left scheme, the number of balls in the fullest bin will be 
\[
\frac{\ln\ln n}{d \ln \Phi_d} \pm \Theta(1)
\]
w.h.p.
\end{theorem}

\begin{theorem}
\label{theorem:algm}
Consider any sequence of insertions and deletions s.t.~at most $hn$ balls are in the bins at any time. If the balls are placed into bins by the Greedy algorithm, at any time $t$ the maximum load is at most 
\[
\frac{\ln\ln n}{d \ln \Phi_d} + O(h)
\]
w.h.p.
\end{theorem}

\section{Analysis}
\label{sec:analysis}
In this section, we will prove Theorems \ref{theorem:greedy}, \ref{theorem:agln} and \ref{theorem:algm} in detail, using \emph{witness trees} to provide an upper bound for the event that a bin contains too many balls. We will prove the bounds for $m=n$ for both the Greedy and the Always-go-left scheme in Sections \ref{sec:witnessGreedy} and \ref{sec:AlwaysGoLeft} respectively. However, we use some simplifying assumptions in those two sections to provide a more clear presentation of the proof techniuqe. Section \ref{sec:nondistinctBalls} will extend these proofs to remove the simplifying assumptions we made initially. Section \ref{sec:moreBalls} will extend the proof to cover the heavily loaded case where $m > n$ as well.

@@

\subsection{Witness tree for Greedy}
\label{sec:witnessGreedy}

\subsection{Witness tree for Always-go-left}
\label{sec:witnessAlg}

\subsection{Nondistinct balls}
\label{sec:nondistinctBalls}

\subsection{More balls than bins}
\label{sec:moreBalls}
